Generalized Tractability

### 2023-03-12 GeneralizedTractability_230310.tex
Fred M2 2023 Mac Updates

For $\varepsilon$ taking on all positive values, $j(\varepsilon,d,\vp)$ takes on all values greater than or equal to $j(\infty,d,\vp)$, so
\[
j\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{j,d}^{-1},d,\vp)+1, \qquad \forall j \ge j(\infty,d,\vp).
\]
This implies via our technical assumption \eqref{eq:ptauassume} that
\begin{equation*}
	K_{\vp,\tau}\,T (\lambda_{j,d}^{-1},d,\tau \vp) \ge
	[T(\lambda_{j,d}^{-1},d, \vp)]^\tau
	\ge
	\left[\frac{(j-1)}{C_{\vp}}\right]^\tau \qquad \forall j \ge j(\infty,d,\vp)
\end{equation*}
Summing both sides of the inequality yields and noting that $L(\vp) \le L(\tau\vp)$, it follows that
\begin{multline*}
	\sup_{d\in\naturals} \sum_{j=j(\infty,d,\vp)}^\infty \frac{1}{T (\lambda_{j,d}^{-1},d, \tau \vp)} \le
	\sup_{d\in\naturals} \sum_{j=j(\infty,d,\vp)}^\infty \frac{1}{T (\lambda_{j,d}^{-1},d, \tau \vp)} \\
	\le K_{\vp,\tau}\, C_{\vp}^\tau
	\sum_{j=j(\infty,d,\vp)}^\infty \frac{1}{(j-1)^\tau} \le
	K_{\vp,\tau}\, C_{\vp}^\tau\, \zeta (\tau) < \infty,
\end{multline*}
where $\zeta$ denotes the Riemann zeta function.
This yields \eqref{eq:strong_tractiff3} with $p$ replaced by $\tau p$, and so we see the necessity of $\eqref{eq:strong_tractiff3}$.

Note now that, \peter{for any $d\in\naturals$,}
\[
 j_d^* = \lfloor C_{\vp}\, T(0,d,\vp)\rfloor +1 \le \lfloor C_{\vp}^\tau\, T(0,d,\tau p,\tau q)\rfloor +1.
\]
So, there exists $L(\tau p,\tau q)$ such that
\[
\peter{\sup_{d\in\naturals}}\,\, \sum_{j=\lceil L(\tau p,\tau q) T(0,d,\tau p,\tau q)\rceil}^\infty \frac{1}{T(\lambda_{j,d}^{-1},d, \tau p,\tau q)}<\infty.
\]

This yields \eqref{eq:tractiff4} with $p$ replaced by $\tau p$ and $q$ and $q_1$ replaced by $\tau q$, and so we see the necessity of $\eqref{eq:tractiff4}$.

>>>>

For $\varepsilon$ taking on all positive values, $j(\varepsilon,d,\vp)$ takes on all values greater than or equal to $j(\infty,d,\vp)$, so
\[
j\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{j,d}^{-1},d,\vp)+1, \qquad \forall j \ge j(\infty,d,\vp).
\]
This implies via our technical assumption \eqref{eq:ptauassume} that
\begin{equation*}
	K_{\vp,\tau}\,T (\lambda_{j,d}^{-1},d,\tau \vp) \ge
	[T(\lambda_{j,d}^{-1},d, \vp)]^\tau
	\ge
	\left[\frac{(j-1)}{C_{\vp}}\right]^\tau \qquad \forall j \ge j(\infty,d,\vp)
\end{equation*}
Summing both sides of the inequality yields and noting that $L(\vp) \le L(\tau\vp)$, it follows that
\begin{multline*}
	\sup_{d\in\naturals} \sum_{j=j(\infty,d,\vp)}^\infty \frac{1}{T (\lambda_{j,d}^{-1},d, \tau \vp)} \le
	\sup_{d\in\naturals} \sum_{j=j(\infty,d,\vp)}^\infty \frac{1}{T (\lambda_{j,d}^{-1},d, \tau \vp)} \\
	\le K_{\vp,\tau}\, C_{\vp}^\tau
	\sum_{j=j(\infty,d,\vp)}^\infty \frac{1}{(j-1)^\tau} \le
	K_{\vp,\tau}\, C_{\vp}^\tau\, \zeta (\tau) < \infty,
\end{multline*}
where $\zeta$ denotes the Riemann zeta function.

Note now that, \peter{for any $d\in\naturals$,}
\[
 j(\infty,d,\vp) = \lfloor C_{\vp}\, T(0,d,\vp)\rfloor +1 \le \lfloor C_{\vp}^\tau\, T(0,d,\tau \vp)\rfloor +1.
\]
So, there exists $L(\tau \vp)$ such that
\[
\peter{\sup_{d\in\naturals}}\,\, \sum_{j=\lceil L(\tau \vp) T(0,d,\tau \vp)\rceil}^\infty \frac{1}{T(\lambda_{j,d}^{-1},d, \tau\vp)}<\infty.
\]
\fred{Fred:  Not sure how $C_{\vp}^\tau$ becomes $L(\tau \vp)$?}

This yields \eqref{eq:tractiff4} with $\vp$ replaced by $\tau \vp$, and so we see the necessity of $\eqref{eq:tractiff4}$.

\bigskp

\noindent \textbf{Optimality:}
\fred{Not sure how to make optimality works because for sufficiency $\vp$ turns into $2\vp$.}
